---
title: "wine"
author: "Jacob Yeung"
date: "4/6/2020"
output: html_document
---

```{r setup, include=TRUE}
knitr::opts_chunk$set(echo = TRUE)
library(glmnet)
library(caret)
data = read.csv('../winequality-red.csv', header = TRUE, sep = ";")
y = data$quality
x = cbind(fixed.acidity = data$fixed.acidity, volatile.acidity = data$volatile.acidity, citric.acid = data$citric.acid, residual.sugar = data$residual.sugar, chlorides = data$chlorides, free.sulfur.dioxide = data$free.sulfur.dioxide, total.sulfur.dioxide = data$total.sulfur.dioxide, density = data$density, pH = data$pH, sulphates = data$sulphates, alcohol = data$alcohol)
```

## Ordinary Least Squares

```{r}
xols = cbind(intercept = 1, x)
olsresults = solve(t(xols)%*%xols)%*%(t(xols)%*%y)
```

The intercept and coefficients for the linear model created by ordinary least squares.

```{r}
olsresults
```

## Ridge Regression

```{r ridge regression}
rrcvfit = cv.glmnet(x, y, alpha = 0, intercept = TRUE)
plot(rrcvfit, main = "Lambda (Tuning) vs MSE")
rrbestlambda = rrcvfit$lambda.min
rrresults = glmnet(x, y, lambda = rrbestlambda, alpha = 0, intercept = TRUE)
```

The minimum cross-validation error lambda value.

```{r}
rrbestlambda
```

The intercept and coefficients for the linear model created by ridge regression.  

```{r}
coef(rrresults)
```

## Lasso Regression

```{r lasso regression}
lrcvfit = cv.glmnet(x, y, alpha = 1, intercept = TRUE)
plot(lrcvfit, main = "Lambda (Tuning) vs MSE")
lrbestlambda = lrcvfit$lambda.min
lrresults = glmnet(x, y, lambda = lrbestlambda, alpha = 1, intercept = TRUE)
```

The minimum cross-validation error lambda value.  

```{r}
lrbestlambda
```

The intercept and coefficients for the linear model created by lasso regression.

```{r}
coef(lrresults)
```

## Elastic Net

```{r}
elastic_reg = train(x = x, y = y,
                    method = "glmnet")
encvfit = cv.glmnet(x, y, alpha = elastic_reg$bestTune$alpha, lambda = elastic_reg$finalModel$lambda, intercept = TRUE)
plot(encvfit, main = "Lambda (Tuning for Optimal Alpha) vs MSE")
enresults = glmnet(x, y, lambda = elastic_reg$bestTune$lambda, alpha = elastic_reg$bestTune$alpha, intercept = TRUE)
```

The minimum cross-validation error lambda and alpha value.  

```{r}
elastic_reg$bestTune
```

The intercept and coefficients for the linear model created by elastic net.

```{r}
coef(elastic_reg$finalModel, elastic_reg$finalModel$lambdaOpt)
```

